comgen-outline

### 2017-08-19 paper/comgen-paper.Rmd
minor edits to generics section

Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs. "Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties, as explored through simulation in the **Model predictions** section.
We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} as well as the target-category prevalence $h$ that the speaker model seeks to convey in Eq. \ref{eq:S1} (Expt. 1a).

@@

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are on an alien planet and you come across your favorite kind of animal from Earth. Now try to predict whether or not that animal is female. To get an intuition for your subjective probability, ask yourself "What percentage of that kind of animal is female?".
The answer is probably 50\%. 
Now try to predict whether or not that animal lays eggs (or, "What percentage of that kind of animal lays eggs?").
Depending on what your favorite animal is, the answer is probably either 50\% or 0\% (e.g., if your favorite animal is a dog, there is a 0\% chance that it lays eggs)^[
The subjective probability may, in fact, be non-zero but very small. This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with the alien environment. 
].

This decomposition of the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
We then ask whether a structured, prior model accounts better for this data than an unstructured model.

@@

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the target category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
<!-- However, cue validity requires knowledge of the target category $k$ -->

@@

<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.  -->
<!-- Do a BDA to describe the data in a more compact form. -->
<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq. \ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).  -->
<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content. -->
<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the target category.  -->
<!-- Some properties have priors that are unimodal with low variance (e.g. \textsc{is female}); these properties are present in every kind in almost exactly the same proportion. The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.  -->
<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->

@@

In Expt. 1a, we measured and modeled the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) for different features.
This data also includes informaiton about the target-category prevalence (e.g., how many robins lay eggs).
Using the target-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].

@@

From the prevalence prior data (Expt. 1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet). 
This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*). 
However, large deviations from an account based purely on target-category prevalence remain: Generics in which the target-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).

@@

The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
Unlike the simple regression models based on point-estimates of target-category prevalence and cue validity, this cognitive model has access to the full prior distribution on prevalence $P(h)$.
This model has two other main architectural differences: an information-theoretic decision between producing the generic vs. an information-less alternative and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.

@@

<!-- Our pragmatic speaker model, $S_1$ in Eq. \ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the target category $h'$). -->
We use the empirically estimated target-category prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt. 1a as the listener's prevalence prior $P(h)$.^[
Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
This corresponds to the more general form of the model described in a footnote in the model section. 
With these data, the predictions of these two models are nearly identical.
]
The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).

@@

The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (prevalences, prevalence priors, and the speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
Importantly, the model recapitulates the prevalence prior data (e.g., the prevalence of laying eggs among various species) and the target-category prevalence data (e.g., the prevalence of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1a).
This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the prevalence distributions).

@@

MHT: Outfit fixed-threshold model with noise parameter?

@@

To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
The blue, solid lined distribution corresponds to the speaker's beliefs about the prevalence of the feature for the target category (also in blue).
The grey distribution shows the listener's prior distribution over prevalence of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
It is also the listener $L_0$'s posterior upon hearing the silent utterance.
The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.

<!-- Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which target-category prevalence is not a good indicator of the acceptability (e.g. \emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades). -->
<!-- We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false. -->
<!-- \emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model. -->
<!-- This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context. -->

@@

<!-- \begin{figure} -->
<!-- \centering -->
<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-prevalence-tj.pdf} -->
<!--     \caption{Endorsing familiar generics. (a)  -->
<!--     Prevalence prior distributions empirically elicited for twenty-one animal properties. -->
<!--     Prior distributions summarized by two parameters of a structured Bayesian model: $\phi$----a property's potential to be present in a category----and $\gamma$----the mean prevalence when it is possible for the property to be present in a category. -->
<!--     Inset plots display example empirical prior distributions over prevalence and corresponding $L_1$ model predictions: the posterior after hearing a generic utterance.  -->
<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a target category. -->
<!--     (b) -->
<!--     Human acceptability judgments compared with model predictions (left) and the target-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
<!--     Color denotes target-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
<!--      Error bars denote 95\% Bayesian credible intervals. -->
<!--     } -->
<!--   \label{fig:commongenerics} -->

@@

In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the target category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
Thus, we have shown how these measurements are related to generic endorsement via our model. 
Yet, this evidence is still correlational in nature.
We do not yet know if the variables that we are measuring are causally related to endorsement.
In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the target propensity that the speaker aims to communicate.

@@

<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the target category belong?". This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.  -->

@@

<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013]. -->
<!-- In these experiments, the prevalence considered is only the prevalence of the property for the target category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.  -->
<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance. -->
<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior. -->

@@

(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
This is not an isolated example.
The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
We posit that the weirdness of these examples is the result of a failure of the comparison class.
<!-- Specifically, the target category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->

Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
From the taxonomic relation of the subordinate categories (e.g., types of books) to the target category (i.e., books), the true prevalence of the feature among the target category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Birds are female".

>>>>

Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs. "Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties, as explored through simulation in the **Model predictions** section.
We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} and the prevalence of the category that the speaker model seeks to convey (the *referent-category* prevalence) $h$ in Eq. \ref{eq:S1} (Expt. 1a).

@@

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; If you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature we are thinking of. ^[
The subjective probability may, in fact, be non-zero in what we're calling as 0\%, non-zero but very small. This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a foreign environment. 
].

This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$.
We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
We measured prior distributions empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
After measurement, we show that assuming a structured model of the prior data is substantially preferred to an unstructured model.

@@

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
<!-- However, cue validity requires knowledge of the referent-category $k$ -->

@@

<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.  -->
<!-- Do a BDA to describe the data in a more compact form. -->
<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq. \ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).  -->
<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content. -->
<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the referent-category.  -->
<!-- Some properties have priors that are unimodal with low variance (e.g. \textsc{is female}); these properties are present in every kind in almost exactly the same proportion. The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.  -->
<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->

@@

In Expt. 1a, we measured and modeled the prevalence prior distribution (e.g., the prevalence of laying eggs for different kinds of animals) for different features.
This data also includes information about the referent-category prevalence (e.g., how many robins lay eggs).
Using the referent-category prevalence as $h$ in our speaker model (Eq. \ref{eq:S1}), the speaker model will predict endorsements for the corresponding generic statements (e.g., "Robins lay eggs").
To test these predictions, we collect human endorsements for thirty generic statements taken from the linguistic and psychological literature on generics [@Prasada2013].

@@

From the prevalence prior data (Expt. 1a), we estimate participants' beliefs about the prevalence of a property for the target categories (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}.
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ref{fig:generics-endorsement-figure}, upper-right: lower-left facet). 
This is because our stimulus set includes generics that are true with high-prevalence properties (e.g., *Leopards have spots.*) and generics that are false with low prevalence properties (e.g., *Leopards have wings.*). 
However, large deviations from an account based purely on referent-category prevalence remain: Generics in which the referent-category has intermediate prevalence (prevalence quartiles 2 and 3: $`r round(100*intermediate.prev.quantiles[["25%"]])`\% < \text{prevalence} < `r  round(100*intermediate.prev.quantiles[["76%"]])`\%$), are not at all explained by prevalence within those categories ($r_{Q2,3}^2(`r r2.gen.n.intermedprev`) = `r r2.gen.regression.prev.intermedprev`$; MSE = $`r mse.gen.regression.prev.intermedprev`$).

@@

The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
Unlike the simple regression models based on point-estimates of referent-category prevalence and cue validity, this cognitive model has access to the full prior distribution on prevalence $P(h)$.
This model has two other main architectural differences: an information-theoretic decision between producing the generic vs. an information-less alternative and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.

@@

<!-- Our pragmatic speaker model, $S_1$ in Eq. \ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the prevalence of the property within the referent-category $h'$). -->
We use the empirically estimated referent-category prevalence as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt. 1a as the listener's prevalence prior $P(h)$.^[
Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
This corresponds to the more general form of the model described in a footnote in the model section. 
With these data, the predictions of these two models are nearly identical.
]
The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).

@@

The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (prevalences, prevalence priors, and the speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
Importantly, the model recapitulates the prevalence prior data (e.g., the prevalence of laying eggs among various species) and the referent-category prevalence data (e.g., the prevalence of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1a).
This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the prevalence distributions).

@@

\mht{Outfit fixed-threshold model with noise parameter?}

@@

To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
The blue, solid lined distribution corresponds to the speaker's beliefs about the prevalence of the feature for the referent-category (also in blue).
The grey distribution shows the listener's prior distribution over prevalence of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ref{fig:generic-endorsement-priors-figure}).
It is also the listener $L_0$'s posterior upon hearing the silent utterance.
The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distrubtion. 
Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.

<!-- Generics that received definitive agreement or disagreement are predicted to be judged as such by the model (corners of Figure \ref{fig:commongenerics}b), including items for which referent-category prevalence is not a good indicator of the acceptability (e.g. \emph{Mosquitos carry malaria}, for prevalence quartiles 2 and 3, $r_{Q2,3}^2=0.955$; MSE=0.005; Figure \ref{fig:commongenerics}b, intermediate shades). -->
<!-- We also see the generics truth judgment model predicts uncertain truth judgments: for instance, \emph{Robins are female} is judged by both the model and human participants to be neither true nor false. -->
<!-- \emph{Sharks don't attack swimmers}, while true of most sharks, is judged to be not a good thing to say by both participants and the model. -->
<!-- This is strong evidence that the puzzling flexibility of generic truth conditions can be understood with a simple but underspecified semantics for which the precise meaning is resolved with respect to diverse prior beliefs in context. -->

@@

<!-- \begin{figure} -->
<!-- \centering -->
<!--     \includegraphics[width=\columnwidth]{figs/generics-prior-prevalence-tj.pdf} -->
<!--     \caption{Endorsing familiar generics. (a)  -->
<!--     Prevalence prior distributions empirically elicited for twenty-one animal properties. -->
<!--     Prior distributions summarized by two parameters of a structured Bayesian model: $\phi$----a property's potential to be present in a category----and $\gamma$----the mean prevalence when it is possible for the property to be present in a category. -->
<!--     Inset plots display example empirical prior distributions over prevalence and corresponding $L_1$ model predictions: the posterior after hearing a generic utterance.  -->
<!--     Intervals on the top of insets show human judgments about the prevalence of the property within a referent-category. -->
<!--     (b) -->
<!--     Human acceptability judgments compared with model predictions (left) and the referent-category prevalence (right) for thirty generic utterances about familiar animals and properties.  -->
<!--     Color denotes referent-category prevalence of the property, with lighter colors indicating higher prevalence.  -->
<!--      Error bars denote 95\% Bayesian credible intervals. -->
<!--     } -->
<!--   \label{fig:commongenerics} -->

@@

In explaining the variable endorsements of generics, we measured the prior distribution over the prevalence of features across categories in addition to the prevalence of the feature in the referent-category (e.g., the percentage of robins that lay eggs) to model the endorsement data.
Thus, we have shown how these measurements are related to generic endorsement via our model. 
Yet, this evidence is still correlational in nature.
We do not yet know if the variables that we are measuring are causally related to endorsement.
In our second case study, we extend our theory to a new domain and provide the first causal evidence for our theory by manipulating the target propensity that the speaker aims to communicate.

@@

<!-- One might also question the feature of our computational model that the speaker is explicitly trying to communicate $h$, her subjective probability.  -->
<!-- We note that if the prevalence prior is structured, as we have argued throughout, then the Question Under Discussion that our speaker model is addressing can also be formalized to be "What component of the prior does the referent-category belong?". This model with a modified QUD makes almost identical quantitative predictions as the simple model without this abstract QUD.  -->

@@

<!-- There have been numerous demonstrations arguing that statistics (e.g., property prevalence) are insufficient to explain generic meaning [@Gelman2002; @Gelman2007; @Cimpian2010; @Cimpian2010c; @Khemlani2012; @Prasada2013]. -->
<!-- In these experiments, the prevalence considered is only the prevalence of the property for the referent-category [e.g., the percentage of birds that lay eggs; @Khemlani2012; @Prasada2013], what we have referred to as \emph{within-kind prevalence}.  -->
<!-- Indeed, this simple statistic also fails to explain our data (Figure \ref{fig:commongenerics}b, right). -->
<!-- Our formal model of pragmatics, by contrast, considers not only within-kind prevalence, but a listener's prior beliefs about prevalence across kinds in order to arrive at a meaning for a generic utterance. -->
<!-- By establishing the validity of a semantics based on prevalence alone, we provide a formalism to learn about categories from generic statements.  -->
<!-- Further, since prevalence is a probability, our model can take information conveyed with a generic and be naturally extended to make predictions about entities in the world or support explanations of events or behavior. -->

@@

(1) is often used to demonstrate that the property prevalence is not sufficient for a generic to be true.
The vast majority of books that exist are paperbacks; nonetheless *Books are paperbacks* sounds weird.
This is not an isolated example.
The same features can be observed in *Pastas are spaghetti*, *Animals are humans*.
These examples are generated by pairing a superordinate category with a property that describes a strictly subordinate category. 
We posit that the weirdness of these examples is the result of a failure of the comparison class.
<!-- Specifically, the referent-category K in a generic statement "Ks F" is not expected to be in the comparison class.  -->

Though we have not introduced a theory of how a comparison class is contructed, relevant ideas may be found in @Keil1979.
His notion of *predicability* might relate to the comparison class, insofar as both may be derived with respect the property (e.g., the kinds of categories can be felicitiously predicated by "is paperback" may form a comparison class).
Note that this idea is similar to @Cohen1999's category of "Relative generics", which have truth conditions that are determined by a comparison to an alternative set of Ks (his Alt(K), our comparison class) which is composed of Ks that could satisfy some F in an an alternative set of Fs.
For example, being a paperback can only be true or false (in the predicability sense of @Keil1979) of individual books.
Aggregations of entities that can be predicated by the feature are, without further supporting context, categories of books.
Such categories may include books of different of different genres or eras, among plausibly many other such sub-categories.
From the taxonomic relation of the subordinate categories (e.g., types of books) to the referent-category (i.e., books), the true prevalence of the feature among the referent-category must be the mean of the prevalence of all subcategories, assuming an equal partitioning of the prior probability of subcategories.
Thus, if we were to construct a speaker model of the statement "Books are paperbacks", the model would predict a 0.5 endorsement: neither true nor untrue, in the same way as "Birds are female".
